### 2023-01-16 proposal-documents/white-paper/white-paper-phd-proposal.tex
white paper phd

%%%%% header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize Name}
\chead{\scriptsize \textit{PhD White Paper Project Proposal}}
\rhead{\scriptsize \today}
\rfoot{\thepage}
%%%%%

@@

{\centering 
    \textbf{Title\\
    PhD White Paper Project Proposal\\
    }
    \vspace{0.10in}
    Name\\
    University\\
    Department
\par
}

@@

\section*{Overall objectives}

\section*{Motivation}

\subsection*{Context}

\section*{Relevant background}

\section*{Importance and relevance to objectives}

@@

\begin{scriptsize}
\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
%        \captionsetup{margin=-9pt}
        \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
        \label{tab-timeline}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}&
        \multicolumn{4}{|c|}{\textbf{Y4}}
        \\
        \cline{2-17}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}
        \\
        \hline
        I. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        II. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        III. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        IV. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        V. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        VI. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        VII.
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        &\x\textbf{X} 
        &\x\textbf{X} 
        \\
        \hline
        XX. Lessons learned
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XX. Future work
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XX. Reprod. \& validation
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &\x
        &\x
        \\
        \hline
\end{longtable}
\end{scriptsize}

>>>>

%%%%% header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize Name}
%\lhead{\scriptsize PNUCENE-D-22-xxxxx}
\chead{\scriptsize \textit{PhD White Paper Project Proposal}}
\rhead{\scriptsize \today}
\rfoot{\thepage}
%%%%%

@@

{\centering 
    \textbf{Title\\
    PhD White Paper Project Proposal\\
    }
    Name\\
    University of Idaho $\sq$ Idaho Falls Center for Higher Education\\
    Department of Nuclear Engineering and Industrial Management
\par
}

@@

\section*{Overall objective}

\section*{Motivation}
\subsection*{Context}

@@

{\small
\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|}
%        \captionsetup{margin=-9pt}
        \caption*{\textbf{Timeframe for execution of proposed project.}}
        \label{tab-timeline}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}&
        \multicolumn{5}{|c|}{\textbf{MONTH}}
        \\
        \cline{2-6}
        &
        \textbf{JAN}&
        \textbf{FEB}&
        \textbf{MAR}&
        \textbf{APR}&
        \textbf{MAY}
        \\
        \hline
        I.
        &\x
        &
        &
        &
        &
        \\
        \hline
        II.
        &\x
        &
        &
        &
        &
        \\
        \hline
        III.
        &\x
        &
        &
        &
        &
        \\
        \hline
        IV.
        &\x
        &
        &
        &
        &
        \\
        \hline
        V.
        &\x
        &
        &
        &
        &
        \\
        \hline
        VI.
        &\x
        &
        &
        &
        &
        \\
        \hline
        VII.
        &
        &
        &
        &
        &\x
        \\
        \hline
        XX. Lessons learned
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XX. Future work
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XX. Reprod. \& validation
        &
        &
        &
        &\x
        &\x
        \\
        \hline
\end{longtable}
}
